% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[letterpaper]{res} 
\usepackage{multicol}
\usepackage[pass]{geometry}
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\renewcommand{\labelitemi}{--}

\begin{document} 

\name{JUSTIN A. EVANKOVICH\\[12pt]}% the \\[12pt] adds a blank

\address{\bf  PRESENT ADDRESS \\ 51280 Blue Top Cabin Rd \\ Houghton, MI 49931}
\address{\bf PERMANENT ADDRESS \\ 14200 Stone Jug Road \\  Battle Creek, MI 49015 \\  (269) 262-6098 \\ jaevanko@mtu.edu}
                                  
\begin{resume}

\section{OBJECTIVE}          
    A summer internship in Computer Engineering or Electrical Engineering.          
 
\section{EDUCATION}          
    Michigan Technological University, Houghton, MI  \\        
    BS Electrical Engineering and Computer Engineering, Dec 2018   \\      
    G.P.A. 3.95/4.0          

\section{LEADERSHIP \& TEAMWORK EXPERIENCE}
	Member of MTU Aerospace Enterprise \\
	Captain for BCAMSC Robotics Team \\
	Worked with Small Mock Engineering Team for Class \\
	Member of High School Band

%\section{COMMUNICATION SKILLS}
	%Environmental Biology Research
	%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
		%\item Collected water samples and performed quality tests
		%\item Wrote research paper with partner
		%\item Presented findings to medium-sized group
	%\end{itemize}

        %Analytical Chemistry Research
        %\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
                %\item Worked largely independently in lab setting
                %\item Presented findings with written report
                %\item Presented findings to medium-sized group
        %\end{itemize}

\section{EXPERIENCE}
   \vspace{-0.15in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
   {\bf Research Assistant.} \>MTU Aerospace Enterprise \> ~~~~~~ Fall 2016 - Present\\
                          \>Houghton, MI
   \end{tabbing}\vspace{-10pt}
   \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
   \item Worked on the Auris Payload subteam.
   \item In the process of choosing GNSS antenna hardware.
   \end{itemize}

   \vspace{-0.15in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
   {\bf Research Assistant.} \>MTU Electrical Engineering Dept. \> ~~~~~~ Spring 2016\\
                          \>Houghton, MI
   \end{tabbing}\vspace{-10pt}
   \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
   \item I primarily developed tools for data collection.
   \item Atmospheric research; turbulence modelling.
   \end{itemize}

   \vspace{-0.15in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Computer Support} \>Tailor Made Property Services \> ~~~~~~ 2012-2014\\
                          \>Battle Creek, MI
   \end{tabbing}\vspace{-10pt}
   \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
   \item Set up computer systems and assisted with general troublshooting.
   \item Worked with little supervision.
   \item Irregular hours; by need.
   \item Family business.
   \end{itemize}

\section{PROJECTS}
	\begin{itemize}
		\item Designed and built a simple VLF radio on protoboard.
	\end{itemize}

\section{TECHNICAL SKILLS}
	\vspace{-1pt}
	\begin{multicols}{4}
	\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
		\item C
		\item Verilog
		\item Java
		\item Haskell
		\item Circuit Analysis
		\item Research Skills
		\item Linux
		\item Unix
		\item MATLAB
		\item Siemens NX
		\item Microsoft Office
		\item LaTeX
	\end{itemize}
	\end{multicols}

\section{HONORS AND AWARDS}
	\begin{itemize}
		\item Certificate of Merit --- MTU Mathematical Sciences
		\item Dean's List 2014--2015
	\end{itemize}

\end{resume}
\end{document}
